### 2023-04-09 chapter1/chapter1_supporting.tex
Clarified wording around fitting matrices
Adjusted spacing in clusters figure to make x-axis more readable

\begin{figure}[h!]
\includegraphics[width=\textwidth]{clusters/out/clusters.png}
\centering
\caption{\textbf{Statistics of orthologous groups.}
\textbf{(A)} Each species is equally represented in orthologous groups (OGs). \textbf{(B)} A plurality of orthologous groups contain all species. \textbf{(C)} Nearly all proteins are associated with a single orthologous group. \textbf{(D)} The number of orthologous groups associated with a species is strongly correlated with the number of unique annotated proteins, which suggests the annotation pipeline generally identifies conserved genes.}
\label{sfig:clusters}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{trees/out/trees2_LG.png}
\centering
\caption{\textbf{Phylogenetic trees fit by different sampling strategies under LG model.}}
\label{sfig:trees_LG}
\end{figure}

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{clusters/out/clusters.png}
\centering
\caption{\textbf{Statistics of orthologous groups.}
\textbf{(A)} Each species is equally represented in orthologous groups (OGs). \textbf{(B)} Nearly all proteins are associated with a single orthologous group. \textbf{(C)} A plurality of orthologous groups contain all species. \textbf{(D)} The number of orthologous groups associated with a species is strongly correlated with the number of unique annotated proteins, which suggests the annotation pipeline generally identifies conserved genes.}
\label{sfig:clusters}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{trees/out/trees2_LG.png}
\centering
\caption{\textbf{Phylogenetic trees fit to meta-alignments yielded by different sampling strategies under LG model.}}
\label{sfig:trees_LG}
\end{figure}
